Through the eyes of the teacher

### 2021-01-22 paper_1/paper_1.Rmd
minor things

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf
---

@@

```{r demographicspilot1table,,echo=FALSE}

@@

# create a basic table (tibble) using tidyverse functions
demo.quest.table <- quest.raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "mean age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "sd age" = round(sd(age), 2),
            # "experience" = round(mean(experience), 2) # in order for this to work experience must be turned into integer via as.integer, maybe replace , with .
            )

# format and insert table in manuscript
apa_table(
  demo.quest.table,
  caption = "Demographic Information",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )

>>>>

documentclass     : "apa6"
classoption       : "man"
output            : papaja::apa6_pdf # hier kann man auch word irgendwie machen
---

@@

```{r demographicspilot1table,echo=FALSE}

@@

# create a basic table (tibble) using tidyverse functions
demo.quest.table <- quest.raw.data %>%
  filter(what == "head") %>%
  group_by(group) %>%
  summarise(N=n(),
            "male" = sum(gender),
            "M age" = round(mean(age), 2),
            "min age" = min(age),
            "max age" = max(age),
            "sd age" = round(sd(age), 2),
            # "experience" = round(mean(experience), 2) # in order for this to work experience must be turned into integer via as.integer, maybe replace , with .
            )

# format and insert table in manuscript
apa_table(
  demo.quest.table,
  caption = "Demographic Information and Teaching Experience",
  # note = "Write Note here", 
  escape = TRUE, # if TRUE special Latex characters are escaped; if this is turned to F captions cannot be rendered. I don't know why...
  placement = "h", # position of table in page:  exact location (h), at the top (t), bottom (b)
  font_size = "small" # options are tiny, scriptsize, footnotesize, small, normalsize (default), large, Large, LARGE, huge, Huge
  )
